QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-31 Response/Paper_Res.tex
Rev_V7.3

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. The size of task $z_i(t)$ is selected from a discrete set $\Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\}$, where $\theta$ represents the number of these values. Hence, $\lambda_i(t) \in \Lambda \cup \{0\}$ to consider the case that no task has arrived. We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

\underline{Authors' Reply}: (a) Task sizes are chosen from a discrete set as most applications have tasks with predefined sizes. For instance, in image and video processing, tasks are typically divided into standardized sizes [X,XX,XXX]. Therefore, we assume that task sizes are selected randomly and uniformly from this discrete set. To address the reviewer’s comment and to provide further clarity regarding task sizes, we have revised the second paragraph of Section III as follows.

@@

\color{black}
We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{blue}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes. We consider, $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.

>>>>

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{red}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes,~\cite{wang2020intelligent},~\cite{zhang2019toward},~\cite{allahham2022multi}. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.

%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

\underline{Authors' Reply}: (a) Task sizes are chosen from a discrete set as most applications have tasks with predefined sizes. For instance, in image and video processing, tasks are typically divided into standardized sizes~\cite{wang2020intelligent},~\cite{zhang2019toward},~\cite{allahham2022multi}. Therefore, we assume that task sizes are selected randomly and uniformly from this discrete set. To address the reviewer’s comment and to provide further clarity regarding task sizes, we have revised the second paragraph of Section III as follows.

@@

\color{black}
We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{red}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes,~\cite{wang2020intelligent},~\cite{zhang2019toward},~\cite{allahham2022multi}. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.

### 2024-10-31 Revision/Paper_Rev.tex
Rev_V7.3

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{red}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes~\cite{gao2022large}. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

>>>>

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{red}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes,~\cite{wang2020intelligent},~\cite{zhang2019toward},~\cite{allahham2022multi}. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.
